---
title: "Cleaning"
author: "Ye Dam Yi"
date: "2/23/2021"
output: html_document
---

```{r library}
library(tidyverse)
library(haven)

```

```{r read-data}
raw_data <- read_spss("data/raw-data-20200618.sav")
# standardize case 
raw_data <- raw_data %>% 
rename_with(tolower)
```

```{r select-columns}
# select columns
raw_data <- raw_data %>% 
  select(duration__in_seconds_, age, gender, ends_with("name"), contains("page_submit"), ends_with("int"), ends_with("obj"), ends_with("decision"), ends_with("pos"), ends_with("neg"), oposout:snegfeel, gloomy, eggplant, nyc, code:fl_40_do_maleselfperspectivetaking)

# drop more variables that need to be dropped 
# drop two more variables that couldn't be dropped because of the conflict in the select command above re: "Name"
# drop practice related time variables
raw_data <- raw_data %>% 
  select(-(recipientlastname:recipientfirstname))

# drop variables related to practice scenario
practice <- c("203", "204", "300" , "4.3" , "332" , "261" , "370" , "403" , "436")
raw_data <- raw_data %>% 
  select(!contains(practice))
# glimpse(raw_data)

```


##### What I learned about dropping and selecting arguments
I first used some "drop" arguments and "select" arguments together in one select command. This created a problem whereby changing the order of the arguments resulted in different select results. I learned that using "drop" and "select" arguments at the same time is not intuitive. It'd be easier to just select the columns I want. 

I learned that I'd need to logically think through each step that moves towards my goal. There has to be some order of operations of doing "selects" and "not-selects" in the same statement. If I don't understand how the order of operations applies, then I shouldn't do that. 

If I'm dropping several columns, I get the rest left. Then, if I'm selecting A, then all I'll be left with is A. Now, what do I accomplish by dropping the initial columns I dropped? Nothing! So I shouldn't do drops and selects in that order.

```{r restructure-time-data, eval = FALSE}
raw_data <- raw_data %>%   
gather(index, comptime1, q209_page_submit, q307_page_submit, q4.13_page_submit, q339_page_submit, q267_page_submit, q377_page_submit, q410_page_submit, q443_page_submit) %>% 
  gather(index, comptime2, q212_page_submit, q313_page_submit, q4.18_page_submit, q345_page_submit, q273_page_submit, q383_page_submit, q416_page_submit, q449_page_submit ) %>% 
  gather(index, comptime3, q218_page_submit, q319_page_submit, q4.23_page_submit, q351_page_submit, q279_page_submit, q389_page_submit, q422_page_submit, q455_page_submit) %>% 
  gather(index, comptime4, q223_page_submit, q325_page_submit, q4.28_page_submit, q357_page_submit, q285_page_submit, q395_page_submit, q428_page_submit, q461_page_submit)
head(raw_data)
```


```{r rename-variables, eval = FALSE}
# rename 
raw_data <- raw_data %>% 
  rename(comptime = duration__in_seconds_,
         foc = fl_30_do_femaleothercontrol,
         fsc = fl_30_do_femaleselfcontrol,
         fop = fl_30_do_femaleotherperspectivetaking,
         fsp = fl_30_do_femaleselfperspectivetaking,
         moc = fl_40_do_maleothercontrol,
         mop = fl_40_do_maleotherperspectivetaking,
         msc = fl_40_do_maleselfcontrol,
         msp = fl_40_do_maleselfperspectivetaking)

# rename time variables (This part needs to be figured out)
q209_page_submit  q307_page_submit q4.13_page_submit q339_page_submit q267_page_submit q377_page_submit q410_page_submit q443_page_submit 
/make pagesubmit2 from
 q212_page_submit q313_page_submit q4.18_page_submit q345_page_submit q273_page_submit q383_page_submit q416_page_submit q449_page_submit 
/make pagesubmit3 from 
q218_page_submit q319_page_submit q4.23_page_submit q351_page_submit q279_page_submit q389_page_submit q422_page_submit q455_page_submit 
/make pagesubmit4 from  
q223_page_submit q325_page_submit q4.28_page_submit q357_page_submit q285_page_submit q395_page_submit q428_page_submit q461_page_submit 
# give id to data
tibble::rowid_to_column(raw_data, "ID")
```