---
title: "Untitled"
author: "Ye Dam Yi"
date: "2/23/2021"
output: html_document
---

```{r library}
library(tidyverse)
library(haven)

```

```{r read-data}
raw_data <- read_spss("data/raw-data-20200618.sav")
# standardize case 
raw_data <- raw_data %>% 
rename_with(tolower)
glimpse(raw_data)
```

```{r select-columns}
# select columns
raw_data <- raw_data %>% 
  select(duration__in_seconds_, age, gender, ends_with("name"), contains("page_submit"), ends_with("int"), ends_with("obj"), ends_with("decision"), ends_with("pos"), ends_with("neg"), oposout:snegfeel, gloomy, eggplant, nyc, code:fl_40_do_maleselfperspectivetaking)

# drop more variables that need to be dropped 
# drop two more variables that couldn't be dropped because of the conflict in the select command above re: "Name"
# drop practice related time variables
raw_data <- raw_data %>% 
  select(-(recipientlastname:recipientfirstname))

# drop variables related to practice scenario
practice <- c("203", "204","300" , "4.3" , "332" , "261" , "370" , "403" , "436")
raw_data <- raw_data %>% 
  select(!contains(practice))
glimpse(raw_data)

# na

# give id to data
# tibble::rowid_to_column(raw_data, "ID")
```

```{r rename-variables, eval = FALSE}
# standardize case 
raw_data <- raw_data %>% 
rename_with(tolower)
glimpse(raw_data)

# rename 
raw_data <- raw_data %>% 
  rename(duration__in_seconds_  = comptime,
         
         
         )
```
##### What I learned
I first used some "drop" arguments and "select" arguments together in one select command. This created a problem whereby changing the order of the arguments resulted in different select results. I learned that using "drop" and "select" arguments at the same time is not intuitive. It'd be easier to just select the columns I want. 

I learned that I'd need to logically think through each step that moves towards my goal. There has to be some order of operations of doing "selects" and "not-selects" in the same statement. If I don't understand how the order of operations applies, then I shouldn't do that. 

If I'm dropping several columns, I get the rest left. Then, if I'm selecting A, then all I'll be left with is A. Now, what do I accomplish by dropping the initial columns I dropped? Nothing! So I shouldn't do drops and selects in that order.



