---
title: "Untitled"
author: "Ye Dam Yi"
date: "2/23/2021"
output: html_document
---

```{r library}
library(tidyverse)
library(haven)

```

```{r read-data}
raw_data <- read_spss("data/raw-data-20200618.sav")
glimpse(raw_data)
```

```{r select-columns, eval = FALSE}
# select columns 
raw_data <- raw_data %>% 
  select(Duration__in_seconds_, Age, Gender, ends_with("Name"), Q3.3, contains("Page_Submit"), Q260, Q205, ends_with("INT"), ends_with("Int"), ends_with("OBJ"), ends_with("Obj"), ends_with("Decision"), ends_with("Pos"), ends_with("Neg"), OPosOut:SNegFeel, Gloomy, Eggplant, NYC, Code:FL_40_DO_MaleSelfPerspectiveTaking)

# drop two more variables
raw_data <- raw_data %>% 
  select(-(RecipientLastName:RecipientFirstName))

# check data
glimpse(raw_data)

# drop submit info for practice scenarios
raw_data <- raw_data %>% 
  select(-contains("Submit") & contains("203" | "204" | "300" | "307" | "4.5" | "4.13" | "334" | "339" | "261" | "263" | "267" | "370" | "372" | "377" | "")   )


# give id to data
tibble::rowid_to_column(raw_data, "ID")
```
##### I learned that using "drop" and "select" arguments at the same time is not inuitive. It'd be easier to just select the columns I want. 

There has to be some order of operations of doing "selects" and "not-selects" in the same statement. If I don't understand how the order of operations applies, then I shouldn't do that. 

I need to logically think through each step that moves towards my goal. 

If I'm dropping several columns, I get the rest left. Then, if I'm selecting A, then all I have been left with is A. Now, what do I accomplish by dropping the initial columns I dropped? Nothing! So why do I do it?

